We did an amazing thing

### 2023-01-12 paper.tex
Fix some errors, typos and so on

\section{Definitions}
\label{sec:def}
Let $A$ be a set in Euclidean space $\mathbb{R}^n$. A function
$\chi_S(\mathbf{x})$ is called an indicator function for the set $A$ and is
defined as follows:
\begin{equation*}
  \chi_S(\bm{x}) = \left\{
  \begin{array}{ll}
    1 & \quad \bm{x} \in A \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}

@@

We give an image of porous medium in the form of two- or threedimensional bit
array $A$ as the input to our algorithm. In the first stage, we convolve the
input with high-pass filter to extract edges from the image. We use the
following filter kernel $H$ \textcolor{red}{Is there notation for 3x3x3
  ``matrices''?}:
\begin{align}
  H_{ij} &= \frac{1}{6} \left[
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & -8 & 1 \\
      1 & 1 & 1
    \end{array}
    \right] \label{eq:filter-3x3-2d} \\
  H_{ijk} &= \frac{1}{18} \left[
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & 1 & 1 \\
      1 & 1 & 1
    \end{array} ;
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & -24 & 1 \\
      1 & 1 & 1
    \end{array} ;
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & 1 & 1 \\
      1 & 1 & 1
    \end{array}
    \right] \label{eq:filter-3x3-3d}
\end{align}
Here symbol $;$ denotes concatenation along the third dimension. Edge extraction
is performed as follows:
\begin{align*}
  A'_{lm}  &= \left| \sum_i\sum_j A_{l-i, m-j}H_{ij} \right| \quad \text{for 2D} \\
  A'_{lmn} &= \left| \sum_i\sum_j\sum_k A_{l-i, m-j, n-k}H_{ijk} \right| \quad
  \text{for 3D}
\end{align*}
Therefore $A'$ has non-zero elements only in a small area around interface
between phases in $A$.

@@

All in all we get the following algorithm for calculation of $F_{ss}$ function:
\begin{algorithmic}[1]
  \Procedure{surfsurf}{$A$}
  \State $A' \gets A*H$
  \Comment{$A'$ becomes an interface of $A$.}
  \State $\hat{A'} \gets F[A']$
  \Comment{Apply DFT to $A'$.}
  \State \textbf{return} $F^{-1}[ |\hat{A}|^2 / N]$
  \Comment{$N$ is a number of elements in $A$}
  \EndProcedure
\end{algorithmic}

@@

\subsection{Surface-surface function in two-dimensional case}
\label{sec:fss-2d}
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/Fss.png}
  \caption[]{Illustration of how $F_{ss}(\bm{r})$ is calculated. The interface
    between solid and void phases is a solid black curve. This interface
    translated by the vector $\bm{r}$ is show as a red solid curve. Support of
    $f_\Gamma(\bm{x}; \Delta)$ is a dashed ring. Shaded regions contribute to
    the surface-surface function.}
  \label{fig:Fss-explained}
\end{figure}
Let $S$ be some set in $\mathbb{R}^2$ which has a smooth boundary $\Gamma$ in
the sense that the boundary has a tangent line at every point. Now we introduce
a function $f_\Gamma(\bm{x}; \Delta)$:
\begin{equation*}
  f_\Gamma(\bm{x}; \Delta) = \left\{
  \begin{array}{ll}
    1/\epsilon & \quad \rho(\bm{x}, \Gamma) < \Delta \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
Here $\rho(\bm{x}, \Gamma)$ means a closest distance from point $\bm{x}$ to the
boundary $\Gamma$.

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/fss-zoomed.png}
  \caption[]{Zoomed image of intersection between the interface $\Gamma$ and its
    translated version $\Gamma'$. $\phi$ is an angle between tangent lines to
    the interfaces. Surface of dashed area is $\frac{\Delta^2}{\sin \phi}$.}
  \label{fig:fss-zoomed}
\end{figure}
Now define a functional sequence $F_{ss}(\bm{x}; \Delta)$:
\begin{align*}
  F_{ss}(\bm{r}; \Delta) &= \int\int f_\Gamma(\bm{x}; \Delta) f_\Gamma(\bm{x}
  + \bm{r}; \Delta) dx dy \\
  &= \sum_{k=1}^N S_k/\Delta^2
\end{align*}
Here $N$ is a number of intersections of $\Gamma$ with itself translated by a
vector $\bm{r}$ and $S_k$ is a surface of each such intersection (see
\cref{fig:Fss-explained}).
When $\Delta$ tends to zero, the boundary at the point of intersection can
be replaced with a tangent line at the point of intersection
(\cref{fig:fss-zoomed}). We get an expression for a surface of
intersection: $S_k = \frac{\Delta^2}{\sin \phi_k}$ where $\phi_k$ is an
acute angle between tangent lines. Hence, we get the following equation:
\begin{equation}
  F_{ss}(\bm{r}) = \lim_{\Delta \to 0} F_{ss}(\bm{r}; \Delta) =
  \sum_{k=1}^N \frac{1}{\sin \phi_k} \label{eq:fss-2d}
\end{equation}
It's easy to show that
$\lim_{\Delta \to 0} f_\Gamma(\bm{x}; \Delta) = |\nabla \chi_S(\bm{x})|$
and therefore \cref{eq:fss-2d} and \cref{eq:fss} define the same function.

\subsection{Dual numbers and automatic differentiation}
\label{sec:dual}
A ring of dual numbers $D$ is a set of pairs of real numbers $(x, y)$ with two
binary operations: $+$ (addition) and $\cdot$ (multiplication) where
multiplication work according to the following law:
\begin{equation*}
  (x_1, y_1)\cdot(x_2, y_2) = (x_1x_2, x_1y_2 + y_1x_2)
\end{equation*}
It's easy to see that $D$ is commutative.

@@

Elementary functions can be extended to dual numbers using Taylor series. For
example, the exponent function is extended as:
\begin{align*}
  e^{a + b\varepsilon} &= \sum_{k=0}^{\infty}\frac{(a + b\varepsilon)^k}{k!} \\
  &= \sum_{k=0}^{\infty} \frac{a^k + bka^{k-1}\varepsilon}{k!} \\
  &= \sum_{k=0}^{\infty} \frac{a^k}{k!} + b\varepsilon \sum_{k=1}
  \frac{a^{k-1}}{(k-1)!} \\
  &= e^a + e^ab\varepsilon
\end{align*}

Here are some basic rules for working with dual numbers:
\begin{itemize}
\item $(a + b\varepsilon) + (c + d\varepsilon) = (a + b) + (c + d)\varepsilon$
\item $(a + b\varepsilon) (c + d\varepsilon) = ac + (ad + bc)\varepsilon$
\item $\frac{a + b\varepsilon}{c + d\varepsilon} = \frac{a}{c} + \frac{bc - ad}{c^2}$
\item $\exp(a + b\varepsilon) = \exp(a) + b\varepsilon\exp(a)$
\item $\sin(a + b\varepsilon) = \sin(a) + b\varepsilon\cos(a)$
\item $\cos(a + b\varepsilon) = \cos(a) - b\varepsilon\sin(a)$
\item $\tan(a + b\varepsilon) = \tan(a) - \frac{b}{cos^2(a)}\varepsilon$
\end{itemize}

@@

\subsection{Surface-surface function for two-dimensional sets with smooth boundary}
\label{sec:cool-algo}
Here we examine two-dimensional sets with smooth boundary described in
\cref{sec:fss-2d} more closely. Suppose a set $S$ is defined as
$S = \left\{ (x, y) \ | \quad f(x, y) \le T \right\}$ where $f(x, y)$ is some function
differentiable in points where $f(x, y) = T$ and $T$ is some threshold. Let's
calculate surface-surface function for this set at a point $(a, b)$. We find all
intersections between a boundary $\Gamma$ and its translated version by solving a
system of equations
\begin{equation*}
  \left\{
  \begin{array}{l}
    f(x, y) = T \\
    f(x-a, y-b) = T    
  \end{array}
  \right.
\end{equation*}
which can be replaced by one equation
\begin{equation}
  (f(x, y) - T)^2 + (f(x-a, y-b) - T)^2 = 0 \label{eq:inter}
\end{equation}
We denote a set of solutions of this equation as $X$. For every $\bm{x}_i \in X$
we find an angle $\phi_i$ between a normal to the boundary and a normal to
the translated boundary as
\begin{equation}
  \cos \phi_i = \frac{(\nabla f(x,y) \vert_{\bm{x}_i}, \nabla f(x-a,y-b)
    \vert_{\bm{x}_i})}{|\nabla f(x,y) \vert_{\bm{x}_i}| |\nabla f(x-a,y-b)
    \vert_{\bm{x}_i}|} \label{eq:angle}
\end{equation}
Here $(\cdot, \cdot)$ denotes a scalar product. Gradient of $f$ at the point
$x_i$ can be found using automatic differentiation and dual numbers described in
\cref{sec:dual}. Note that acute angle between tangent lines equals to acute
angle between normals, therefore we can find correlation function $F_{ss}(a, b)$
using the following formula:
\begin{equation}
  F_{ss}(a, b) = \sum_i \frac{1}{\sqrt{1 - \cos^2 \phi_i}} \label{eq:fss-method}
\end{equation}

@@

The set $X$ can be found by firstly evaluating $f(x, y)$ in some regular grid
searching for all points $(x_i, y_i)$ for which $|f(x_i, y_i) - T| < \varepsilon$ 
and $|f(x_i - a, y_i - b) - T| < \varepsilon$ for some positive $\varepsilon$
and then using these points as starting points for some gradient descent based
algorithm like ADAM to solve \cref{eq:inter}.

@@

\subsection{A disk}
If we define $f(x, y) = x^2 + y^2$ then an inequation $f(x, y) \le R^2$ defines
a disk of radius $R$ with center at the origin. In this case $F_{ss}$ depends
only on distance $r$ from the origin:
\begin{equation*}
  F_{ss}(r) = \left\{
  \begin{array}{ll}
    \frac{4R^2}{r\sqrt{4R^2-r^2}} & \quad r < 2R \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
A comparison of the algorithm described in \cref{sec:algo} applied to images
with different resolution with a theory is shown on \cref{fig:fss-disk-3x3}.
\begin{figure*}[!pt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/fss-disk-3x3.png}
    \label{fig:fss-disk-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/fss-disk-5x5.png}
    \label{fig:fss-disk-5x5}}
  \caption[]{Plot of surface-surface function for a disk with radius
    $R = 0.0334$. Resolution of the image varies from $100\times 100$ pixels to
    $3100\times 3100$.}
  \label{fig:fss-disk}
\end{figure*}

@@

\section{Results}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/ball-3d-ss.png}
  \caption[]{Surface-surface function calculated for a three-dimensional ball
    with radius $R = 0.24$ using filters $H$ and $H'$. Theoretical curve is
    provided for a comparison. Image dimensions are $450 \times 450 \times 450$.}
  \label{fig:fss-ball}
\end{figure}
With the new filter calculation of $F_{ss}$ becomes more precise, even for
three-dimensional images. This can be seen in comparison with theoretical values
for known cases like the one of a ball. On \cref{fig:fss-ball} there are plots
of $F_{ss}$ function calculated with filters $H$ and $H'$ along with a
theoretical curve. It can be verified that filter $H'$ is better indeed by
calculating
\begin{equation*}
  error = \sqrt{\frac{\sum_i (F_{ss}^{calc}(x_i) -
      F_{ss}^{theory}(x_i))^2}{\sum_i F_{ss}^{theory}(x_i)^2}}
\end{equation*}
where $x_i$ belong to a set
$(\varepsilon, 2R - \varepsilon) \cup (2R + \varepsilon, 1)$ (here we assume
image dimensions to be $1 \times 1 \times 1$ length units). Taking
$\varepsilon = 0.01$ we get $error = 0.006$ for filter $H$ and $error = 0.00017$
for filter $H'$.

>>>>

\section{Definitions}
\label{sec:def}
Let $A$ be a set in Euclidean space $\mathbb{R}^n$. A function
$\chi_A(\mathbf{x})$ is called an indicator function for the set $A$ and is
defined as follows:
\begin{equation*}
  \chi_A(\bm{x}) = \left\{
  \begin{array}{ll}
    1 & \quad \bm{x} \in A \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}

@@

We give an image of porous medium in the form of two- or three-dimensional bit
array $A$ as the input to our algorithm. In the first stage, we convolve the
input with high-pass filter to extract edges from the image. We use the
following filter kernel $H$ \textcolor{red}{Is there notation for 3x3x3
  ``matrices''?}:
\begin{align}
  H_{ij} &= \frac{1}{6} \left[
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & -8 & 1 \\
      1 & 1 & 1
    \end{array}
    \right] \label{eq:filter-3x3-2d} \\
  H_{ijk} &= \frac{1}{18} \left[
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & 1 & 1 \\
      1 & 1 & 1
    \end{array} ;
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & -24 & 1 \\
      1 & 1 & 1
    \end{array} ;
    \begin{array}{ccc}
      1 & 1 & 1 \\
      1 & 1 & 1 \\
      1 & 1 & 1
    \end{array}
    \right] \label{eq:filter-3x3-3d}
\end{align}
Here symbol $;$ denotes concatenation along the third dimension. Edge extraction
is performed as follows:
\begin{align*}
  A'_{lm}  &= \left| \sum_i\sum_j A_{l-i, m-j}H_{ij} \right| \quad \text{for 2D} \\
  A'_{lmn} &= \left| \sum_i\sum_j\sum_k A_{l-i, m-j, n-k}H_{ijk} \right| \quad
  \text{for 3D}
\end{align*}
Therefore $A'$ has non-zero elements only in a small area around interface
between phases in $A$.

@@

All in all we get the following algorithm for calculation of $F_{ss}$ function:
\begin{algorithmic}[1]
  \Procedure{surfsurf}{$A$}
  \State $A' \gets H*A$
  \Comment{$A'$ becomes an interface of $A$.}
  \State $\hat{A'} \gets F[A']$
  \Comment{Apply DFT to $A'$.}
  \State \textbf{return} $F^{-1}[ |\hat{A}|^2 / N]$
  \Comment{$N$ is a number of elements in $A$}
  \EndProcedure
\end{algorithmic}

@@

\subsection{Surface-surface function in two-dimensional case}
\label{sec:fss-2d}
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/Fss.png}
  \caption[]{Illustration of how $F_{ss}(\bm{r})$ is calculated. The interface
    between solid and void phases is a solid black curve. This interface
    translated by the vector $\bm{r}$ is show as a red solid curve. Support of
    $f_\Gamma(\bm{x}; \Delta)$ is a dashed ring. Shaded regions contribute to
    the surface-surface function.}
  \label{fig:Fss-explained}
\end{figure}
Let $S$ be some set in $\mathbb{R}^2$ which has a smooth boundary $\Gamma$ in
the sense that the boundary has a tangent line almost at every point. Now we
introduce a function $f_\Gamma(\bm{x}; \Delta)$:
\begin{equation*}
  f_\Gamma(\bm{x}; \Delta) = \left\{
  \begin{array}{ll}
    1/\Delta & \quad \rho(\bm{x}, \Gamma) < \Delta \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
Here $\rho(\bm{x}, \Gamma)$ means a closest distance from point $\bm{x}$ to the
boundary $\Gamma$.

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/fss-zoomed.png}
  \caption[]{Zoomed image of intersection between the interface $\Gamma$ and its
    translated version $\Gamma'$. $\phi$ is an angle between tangent lines to
    the interfaces. Surface of dashed area is $\frac{\Delta^2}{\sin \phi}$.}
  \label{fig:fss-zoomed}
\end{figure}
Now define a functional sequence $F_{ss}(\bm{x}; \Delta)$:
\begin{align*}
  F_{ss}(\bm{r}; \Delta) &= \int\int f_\Gamma(\bm{x}; \Delta) f_\Gamma(\bm{x}
  + \bm{r}; \Delta) dx dy \\
  &= \sum_{k=1}^N S_k/\Delta^2
\end{align*}
Here $N$ is a number of intersections of $\Gamma$ with itself translated by a
vector $\bm{r}$ and $S_k$ is a surface of each such intersection (see
\cref{fig:Fss-explained}).
When $\Delta$ tends to zero, the boundary at the point of intersection can
be replaced with a tangent line at the point of intersection
(\cref{fig:fss-zoomed}). We get an expression for a surface of
intersection: $S_k = \frac{\Delta^2}{\sin \phi_k}$ where $\phi_k$ is an
acute angle between tangent lines. Hence, we get the following equation:
\begin{equation}
  F_{ss}(\bm{r}) = \lim_{\Delta \to 0} F_{ss}(\bm{r}; \Delta) =
  \sum_{k=1}^N \frac{1}{\sin \phi_k} \label{eq:fss-2d}
\end{equation}
It's easy to show that
$\lim_{\Delta \to 0} f_\Gamma(\bm{x}; \Delta) = |\nabla \chi_A(\bm{x})|$
and therefore \cref{eq:fss-2d} and \cref{eq:fss} define the same function.

\subsection{Dual numbers and automatic differentiation}
\label{sec:dual}
A ring of dual numbers $D$ is a set of pairs of real numbers $(x, y)$ with two
binary operations: $+$ (addition) and $\cdot$ (multiplication) where
multiplication works according to the following law:
\begin{equation*}
  (x_1, y_1)\cdot(x_2, y_2) = (x_1x_2, x_1y_2 + y_1x_2)
\end{equation*}
It's easy to see that $D$ is commutative.

@@

Elementary functions can be extended to dual numbers using Taylor series. For
example, the exponent function is extended as:
\begin{align*}
  e^{a + b\varepsilon} &= \sum_{k=0}^{\infty}\frac{(a + b\varepsilon)^k}{k!} \\
  &= \sum_{k=0}^{\infty} \frac{a^k + bka^{k-1}\varepsilon}{k!} \\
  &= \sum_{k=0}^{\infty} \frac{a^k}{k!} + b\varepsilon \sum_{k=1}^{\infty}
  \frac{a^{k-1}}{(k-1)!} \\
  &= e^a + e^ab\varepsilon
\end{align*}

Here are some basic rules for working with dual numbers (some of which we have
already described):
\begin{itemize}
\item $(a + b\varepsilon) + (c + d\varepsilon) = (a + c) + (b + d)\varepsilon$
\item $(a + b\varepsilon) (c + d\varepsilon) = ac + (ad + bc)\varepsilon$
\item $\frac{a + b\varepsilon}{c + d\varepsilon} = \frac{a}{c} + \frac{bc - ad}{c^2}$
\item $\exp(a + b\varepsilon) = \exp(a) + b\varepsilon\exp(a)$
\item $\sin(a + b\varepsilon) = \sin(a) + b\varepsilon\cos(a)$
\item $\cos(a + b\varepsilon) = \cos(a) - b\varepsilon\sin(a)$
\item $\tan(a + b\varepsilon) = \tan(a) - \frac{b}{cos^2(a)}\varepsilon$
\end{itemize}

@@

\subsection{Surface-surface function for two-dimensional sets with smooth boundary}
\label{sec:cool-algo}
Here we examine two-dimensional sets with smooth boundary described in
\cref{sec:fss-2d} more closely. Suppose a set $S$ is defined as
$S = \left\{ (x, y) \ | \quad f(x, y) \le T \right\}$ where $f(x, y)$ is some function
differentiable at points where $f(x, y) = T$ and $T$ is some threshold. Let's
calculate surface-surface function for this set at a point $(a, b)$. We find all
intersections between a boundary $\Gamma$ and its translated version by solving a
system of equations
\begin{equation*}
  \left\{
  \begin{array}{l}
    f(x, y) = T \\
    f(x-a, y-b) = T    
  \end{array}
  \right.
\end{equation*}
which can be replaced by one equation
\begin{equation}
  (f(x, y) - T)^2 + (f(x-a, y-b) - T)^2 = 0 \label{eq:inter}
\end{equation}
We denote a set of solutions of this equation as $X$. For every $\bm{x}_i \in X$
we find an angle $\phi_i$ between a normal to the boundary and a normal to
the translated boundary as
\begin{equation}
  \cos \phi_i = \frac{(\nabla f(x,y) \vert_{\bm{x}_i}, \nabla f(x-a,y-b)
    \vert_{\bm{x}_i})}{|\nabla f(x,y) \vert_{\bm{x}_i}| |\nabla f(x-a,y-b)
    \vert_{\bm{x}_i}|} \label{eq:angle}
\end{equation}
Here $(\cdot, \cdot)$ denotes a dot product. Gradient of $f$ at the point
$\bm{x_i}$ can be found using automatic differentiation and dual numbers
described in \cref{sec:dual}. Note that acute angle between tangent lines equals
to acute angle between normals, therefore we can find correlation function
$F_{ss}(a, b)$ using the following formula:
\begin{equation}
  F_{ss}(a, b) = \sum_i \frac{1}{\sqrt{1 - \cos^2 \phi_i}} \label{eq:fss-method}
\end{equation}

@@

The set $X$ can be found by firstly evaluating $f(x, y)$ in some regular grid
searching for all points $(x_i, y_i)$ for which $|f(x_i, y_i) - T| < \epsilon$
and $|f(x_i - a, y_i - b) - T| < \epsilon$ for some positive $\epsilon$
and then using these points as starting points for some algorithm based on
gradient descent like ADAM to solve \cref{eq:inter}.

@@

\subsection{A disk}
If we define $f(x, y) = x^2 + y^2$ then an inequation $f(x, y) \le R^2$ defines
a disk of radius $R$ with center at the origin. In this case $F_{ss}$ depends
only on distance $r$ from the origin:
\begin{equation*}
  F_{ss}(r) = \left\{
  \begin{array}{ll}
    \frac{4R^2}{r\sqrt{4R^2-r^2}} & \quad r < 2R \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
A comparison of the algorithm described in \cref{sec:algo} applied to images
with different resolution with a theory is shown on \cref{fig:fss-disk}.
\begin{figure*}[!pt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/fss-disk-3x3.png}
    \label{fig:fss-disk-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/fss-disk-5x5.png}
    \label{fig:fss-disk-5x5}}
  \caption[]{Plot of surface-surface function for a disk with radius
    $R = 0.0334$. Resolution of the image varies from $100\times 100$ pixels to
    $3100\times 3100$.}
  \label{fig:fss-disk}
\end{figure*}

@@

\section{Results}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/ball-3d-ss.png}
  \caption[]{Surface-surface function calculated for a three-dimensional ball
    with radius $R = 0.24$ using filters $H$ and $H'$. Theoretical curve is
    provided for a comparison. Image dimensions are $450 \times 450 \times 450$.}
  \label{fig:fss-ball}
\end{figure}
With the new filter calculation of $F_{ss}$ becomes more precise, even for
three-dimensional images. This can be seen in comparison with theoretical values
for known cases like the one of a ball. On \cref{fig:fss-ball} there are plots
of $F_{ss}$ function calculated with filters $H$ and $H'$ along with a
theoretical curve. It can be verified that filter $H'$ is better indeed by
calculating
\begin{equation*}
  error = \sqrt{\frac{\sum_i (F_{ss}^{calc}(x_i) -
      F_{ss}^{theory}(x_i))^2}{\sum_i F_{ss}^{theory}(x_i)^2}}
\end{equation*}
where $x_i$ belong to a set
$(\epsilon, 2R - \epsilon) \cup (2R + \epsilon, 1)$ (here we assume image
dimensions to be $1 \times 1 \times 1$ length units). Taking
$\epsilon = 0.01$ we get $error = 0.006$ for filter $H$ and $error = 0.00017$
for filter $H'$.
